\documentclass[a4paper, 10pt]{article}

\usepackage[margin = 1in]{geometry} % for spacing around
\usepackage{graphicx} % for including images in your pdfs
\usepackage{xcolor} % for including colors in your pdf
\usepackage{soul} % for text decoration
\usepackage[utf8]{inputenc} % for encoded text
\usepackage[T1]{fontenc}
\usepackage{setspace} % for setting different line spacings between paragrafs.
\usepackage{enumerate} % for letting us get more detailed enumerate lists
\usepackage{multirow} % to let us combine more rows together
\usepackage{colortbl} % for decorating tables
\usepackage{amsmath} % used for representing more complicated math displays
\usepackage{supertabular}
\usepackage{longtable} % both of these packages are used to making really big tables
\usepackage{wrapfig} % allows us to wrap text around figures
\usepackage{fancyhdr} % for making fancy headers
%\usepackage{bibtex} % for making better bibliographies
\usepackage[pdftex]{hyperref} % for letting us make links
\usepackage{lscape} % Allows us to flip from portrait to landspace
\usepackage{tikz} % for high detailed drawing
\usepackage{multicol} % To put things side by side
\usepackage{rotating} % For rotating objects
% \usepackage{draftwatermark} % For adding watermarks
\usepackage{MnSymbol} % for using multiple symbols
\usepackage{mathtools} % Used for more math symbols
\usepackage{xfrac} % For more complciated fractions and to add derivitives
\usepackage{hyperref} % for hyper links

% Setting up the default image path
\graphicspath{{./Pictures/}}

% Implementing authro details
\title{Solutions for Homework7}
\author{Emre Arapcic-Uvak & Vedad Siljic}
\date{}

% Setting up the fancy page style
\fancypagestyle{customStyle}{
	\lhead{} \chead{} \rhead{}
	\lfoot{} \cfoot{\thepage} \rfoot{}
	\renewcommand{\headrulewidth}{0pt}
	\renewcommand{\footrulewidth}{1pt}
}
\pagestyle{customStyle}

% Setting up hyperref options
\hypersetup {
	colorlinks = false,
	citecolor = black,
	filecolor = blue,
	linkcolor = blue,
	urlcolor = blue,
	pdftex
}

\begin{document}
	\maketitle
	\vspace{5mm}
	
	\begin{abstract}
		\begin{center}
			\noindent In this document we will show the solutions for problems represented in the given homework for this week.
		\end{center}
	\end{abstract}
	\pagebreak
	
	\tableofcontents
	\pagebreak
	
	\section{Theoretical Problems}
		\subsection{Part 1.}
			\subsubsection{Question}
				\begin{enumerate}
					\item \noindent Your company has been granted a contract to develop the next generation of electronic cigarette, also 
					known as a “nicotine delivery system,” and you have been assigned to the design team. Can you in good 
					conscience contribute your expertise to this project? Write in details: issues, stakeholders, 
					consequences action you might take
					
					\item Choose \textbf{one}~of the following industries then:
					\begin{enumerate} [a.]
						\item Apply the four-step ethical decision-making procedure to gain insight into the nature of the decision to be made\\
						\noindent (what the issue and who is effected by the alterntives, alternatives from other prespectives and their correlation, suggest an action)
						
						\item Give at least one more ethical issue in the indutry you choose
					\end{enumerate}
				\end{enumerate}
			
			\subsubsection{Solution}
				\begin{enumerate}
					\item 
						\begin{enumerate}
							\item Step 1: Identify and see if there is a problem, and if there is who is affected by it. \\
							\begin{itemize}
								\item Issues:
								\begin{itemize}
									\item Nicotine is very addictive and detrimental for your body.
									\item This device / product might misdirect a lot of people into thinking that it will help them to stop smoking while in reality it could be worse.
									\item Health care lawsuits / Protests against the product.
									\item If this product becomes popular, there will be a huge decline in tobacco sales.
									\item Refusing to make this product can get you fired.
									\item Halting the production can cause huge money loss.
								\end{itemize}
							
								\item Stakeholders:
								\begin{itemize}
									\item Nicotine addicts that are trying to recover
									\item The User
									\item Young people
									\item The company
									\item Tobacco farmers
									\item You
								\end{itemize}
							\end{itemize}
						
							\item Step2: Analyze alternative courses of action from different perspectives.
							\begin{itemize}
								\item Consequences:
								\begin{itemize}
									\item Future lawsuits will come.
									\item You might lose your job.
									\item A lot of people might develop health problems
								\end{itemize}
							
								\item Intent:
								\begin{itemize}
									\item People who struggle with nicotine addiction should \textcolor{red}{\textbf{\textsc{NOT}}} use this product.
									\item People who use this device risk getting addicted to nicotine.
									\item People might overcome their tobacco addiction.
									\item The company will make a lot of \textcolor{green}{\$\$\$}
								\end{itemize}
							
								\item Character
								\begin{itemize}
									
								\end{itemize}
							\end{itemize}
						\end{enumerate}
				\end{enumerate}
	\section{Octave Problems}
\end{document}